### 2025-04-09 cluster-analysis.qmd
20250408 - plotly
20250409 - fix error

ggplotly(plot_qbTiers)
```

@@

ggplotly(plot_rbTiers)
```

@@

ggplotly(plot_wrTiers)
```

@@

ggplotly(plot_teTiers)
```

@@

#names(nfl_players) #gsis_id: height, weight
#names(nfl_combine) #gsis_id: vertical, forty, ht, wt
#names(player_stats_seasonal_offense) #player_id, season: receptions, receiving_air_yards, air_yards_share, target_share
#names(nfl_advancedStatsPFR_seasonal) #gsis_id, season: adot.rec, rec.rec, brk_tkl.rec, drop.rec, drop_percent.rec
#names(nfl_actualStats_offense_career) #player_id: receptions, targets, receiving_air_yards, air_yards_share, target_share
```

@@

# Merge
playerListToMerge <- list(
  nfl_players %>% select(gsis_id, display_name, position, height, weight),
  nfl_combine %>% select(gsis_id, vertical, forty, ht, wt),
  player_stats_seasonal_careerWRs %>% select(player_id, targets_per_season, receptions_per_season, receiving_air_yards_per_season) %>% 
    rename(gsis_id = player_id),
  nfl_actualStats_offense_career %>% select(player_id, receptions, targets, receiving_air_yards, air_yards_share, target_share) %>% 
    rename(gsis_id = player_id),
  nfl_advancedStatsPFR_career %>% select(gsis_id, adot.rec, rec.rec, brk_tkl.rec, drop.rec, drop_percent.rec)
)

>>>>

plotly::ggplotly(plot_qbTiers)
```

@@

plotly::ggplotly(plot_rbTiers)
```

@@

plotly::ggplotly(plot_wrTiers)
```

@@

plotly::ggplotly(plot_teTiers)
```

@@

# names(nfl_players) #gsis_id: height, weight
# names(nfl_combine) #gsis_id: vertical, forty, ht, wt
# names(player_stats_seasonal_offense) #player_id, season: receptions, receiving_air_yards, air_yards_share, target_share
# names(nfl_advancedStatsPFR_seasonal) #gsis_id, season: adot.rec, rec.rec, brk_tkl.rec, drop.rec, drop_percent.rec
# names(nfl_actualStats_career_player_inclPost) #player_id: receptions, targets, receiving_air_yards, air_yards_share, target_share
```

@@

# Merge
playerListToMerge <- list(
  nfl_players %>% select(gsis_id, display_name, position, height, weight),
  nfl_combine %>% select(gsis_id, vertical, forty, ht, wt),
  player_stats_seasonal_careerWRs %>% select(player_id, targets_per_season, receptions_per_season, receiving_air_yards_per_season) %>% 
    rename(gsis_id = player_id),
  nfl_actualStats_career_player_inclPost %>% select(player_id, receptions, targets, receiving_air_yards, air_yards_share, target_share) %>% 
    rename(gsis_id = player_id),
  nfl_advancedStatsPFR_career %>% select(gsis_id, adot.rec, rec.rec, brk_tkl.rec, drop.rec, drop_percent.rec)
)
